Reanalysis Step 5: Main Effects Outcome Analysis

### 2025-09-04 reanalysis-5-outcome_analysis.qmd
force refit

# CACHE SETTINGS - Set these to TRUE to force recalculation
force_refit_models <- FALSE  # Set to TRUE to re-fit all models
force_recalc_emmeans <- TRUE  # Set to TRUE to recalculate marginal means

>>>>

# CACHE SETTINGS - Set these to TRUE to force recalculation
force_refit_models <- TRUE  # Set to TRUE to re-fit all models
force_recalc_emmeans <- TRUE  # Set to TRUE to recalculate marginal means
